Review stages

### 2024-06-07 doc/review-stages.qmd
updated tasks for review stages

-   first skimming the papers and group by themes, writing a basic
    free-hand summary
-   then read a few from each theme to decide on what information to
    extract
-   then discuss together the themes to group by and information to
    extract
-   then we follow what we agreed on

>>>>

-   first skimming the papers and group by themes, writing a basic
    free-hand summary
-   then read a few papers from each theme to decide on what information
    to extract
-   then discuss together the themes to group by and information to
    extract

## Data extraction

-   we make a data extraction template
-   extract data and read the papers
